Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging

### 2020-06-05 article.tex
Edits and implemented Andy's changes

\author[a]{Colin T. Sullender}
\author[b]{Fei He}
\author[b,c]{Chong Xie}
\author[b,c]{Lan Luan}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, University of Texas at Austin, 107 W. Dean Keeton Street Stop C0800, Austin, Texas, 78712, United States}
\affil[b]{Department of Electrical and Computer Engineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
\affil[c]{Department of Bioengineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}

@@

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology. In this paper, we characterize the impact of isoflurane during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI) of cerebral blood flow (CBF). We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions. Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchymal perfusion. These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
\end{abstract}

@@

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser-Doppler flowmetry (LDF), and intrinsic signal optical imaging (ISOI) have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy (2PLM) showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. To date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm. Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of ~2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.

The 15 raw intensity images were converted to spatial speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7x7-pixel window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
%
% Equation 1 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K(T,\tau_c) =
        \left(
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \beta(1 - \rho)^2 +
        \nu_{ne} +
        \nu_{noise}
        \right)^{1/2}
\end{equation}

@@

Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}. Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event \cite{Kazmi:2015du}. This is achieved by scaling the fitted $ICT$ value by the caliber of the vessel ($d_{vessel}$) in order to obtain an estimate of "vascular flux” that accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}. This paper utilizes the “flux” metric (arbitrary units) for all vascular measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.

@@

\subsection{Animal Preparation}
Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River) were anesthetized with medical O2 vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts). Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific). Mice were placed supine in a stereotaxic frame (Kent Scientific) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure. The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates. A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion. A 3 mm round cover glass (\#1, World Precision Instruments) was placed over the exposed brain with artificial cerebrospinal fluid filling the void. Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments) was deposited to bond the glass to the skull. A layer of C\&B-Metabond (Parkell Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure. A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements. The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging. They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear, belt-driven treadmill awake imaging system \cite{He:2020}.

Mice were housed 1-4 per cage in a conventional vivarium maintained at 20 $^\circ$C on 12-hour light-to-dark cycles (07:00 to 19:00). All subjects received standard cage supplements (e.g. cage enclosures, nesting material, and wooden toys) with water and food \textit{ad libitum}. All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin (AUP-2018-00021).

@@

Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2\% to induce anesthesia. After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function. After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

An additional subject ($n = 1$) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics. Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery. The four repeated imaging sessions for this subject were spaced at least one week apart to avoid any complications from extended anesthesia exposure.

@@

The systematic changes caused by general anesthesia are shown in Fig.~\ref{fig:system_image}b and Video 1. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in cerebral blood flow caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}. Dilation can be seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature precluded the generation of full-field relative flow change maps.

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure1.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:system_image}
        (a) MESI system schematic with 2x magnification. L1 (f = 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology), and L2 (f = 100 mm, Achromatic Doublet, AC254-100-A, Thorlabs). (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
    }
\end{figure}

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session. The open source image registration toolbox Elastix \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery in order to account for motion-related displacements. A central moving average filter ($k = 5$) was also applied to smooth the fitted data for presentation. The change in diameter of the two vessels (R1 and R2) was estimated using the full-width at half-maximum (FWHM) of a Gaussian fit to the vascular cross-sections extracted from the 5 ms exposure speckle contrast frames (Fig.~\ref{fig:acute}b). The width of the two vessels remained steady throughout the awake measurements but increased while under anesthesia, with the larger vessel (R1) growing by over 50\%. This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c). The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%. Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) exhibit the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:acute}
        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Timecourses of (b) vessel caliber and (c) relative change in blood flow within the regions over an extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel caliber, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four days (mean $\pm$ sd).
    }
\end{figure}

The repeatability of these measurements are further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}. Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states over three separate imaging sessions lasting 30 minutes each. Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the hemodynamics. On average, vessel width increased by 10-20\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1\%) and therefore a smaller increase in vascular flux (+60\%). The perfusion of parenchymal regions increased on average by at least 50\% across all subjects.

% Figure 3 - Awake to Anesthetized Results Summary
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure3.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:summary}
        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Each row of charts depicts average vessel caliber, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states across three different imaging sessions for each animal (mean $\pm$ sd).
    }
\end{figure}

@@

Much larger changes in blood flow were measured in the surface vessels, with vascular flux increasing on average by 135 $\pm$ 64\% across all trials. Even vessels that experienced only minimal vasodilation, such as R2 for Subject 1 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow. Because few imaging modalities are capable of measuring the dynamics of blood flow with sufficient spatial resolution to distinguish individual vessels, there has been limited work on this topic in awake animals. A lone study using LDF found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}. However, because large blood vessels were avoided, the LDF likely sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged by MESI. The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by LDF, so direct comparisons may not technically be possible \cite{Kazmi:2015du}.

@@

While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj, Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}. Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a range of flow rates \cite{Parthasarathy:2008el}. Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the visible surface vasculature. Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:acute}c would have measured only a 140\% increase in the large vessel instead of 267\%. The repeatability of the day-to-day measurements further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.

The effects of isoflurane fundamentally undermine the imaging of cortical hemodynamics in the normal physiological state. Blood flow imaging techniques such as LSCI, LDF, and fMRI require greater sensitivity because of the suppression of the hemodynamic response \cite{Takuwa:2012ee} and measure a delayed neurovascular coupling \cite{Pisauro:2013cx}. Anatomical imaging with two-photon microscopy only captures heavily-dilated vasculature unrepresentative of the awake resting state \cite{Lyons:2016bd}. The consistency and reliability of all imaging techniques can suffer from the effects of prolonged isoflurane exposure, which can cause continual vasodilation as seen in Fig.~\ref{fig:acute}b. This may result in extended imaging sessions documenting disparate anatomies and physiologies between the beginning and conclusion of an experiment.

>>>>

\author[a]{Colin T. Sullender}
\author[a]{Lisa M. Richards}
\author[b]{Fei He}
\author[b,c]{Chong Xie}
\author[b,c]{Lan Luan}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, University of Texas at Austin, 107 W. Dean Keeton Street Stop C0800, Austin, Texas, 78712, United States}
\affil[b]{Department of Electrical and Computer Engineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
\affil[c]{Department of Bioengineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}

@@

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology. In this paper, we characterize the impact of isoflurane on cerebral blood flow (CBF) during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI). We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions. Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchymal perfusion. These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
\end{abstract}

@@

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser-Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy (2PLM) showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. To date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm. Fifteen camera exposures ranging between 50 $\mu$s and 80 ms {Parthasarathy:2008el, Atchia:2013ep, Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.

The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7x7-pixel window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
%
% Equation 1 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K(T,\tau_c) =
        \left(
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \beta(1 - \rho)^2 +
        \nu_{ne} +
        \nu_{noise}
        \right)^{1/2}
\end{equation}

@@

Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}. Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event \cite{Kazmi:2015du}. This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}. This paper utilizes the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.

@@

\subsection{Animal Preparation}

Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical O2 vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.). Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific Corp.). Mice were placed supine in a stereotaxic frame (Kent Scientific Corp.) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure. The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates. A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion. A 3 mm round cover glass (\#1, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void. Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull. A layer of C\&B-Metabond (Parkell, Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure. A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements. The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging. They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear, belt-driven treadmill awake imaging system \cite{He:2020}.

Mice were housed 1-4 per cage in a conventional vivarium maintained at 20 $^\circ$C on 12-hour light-to-dark cycles (07:00 to 19:00). All subjects received standard cage supplements (e.g. cage enclosures, nesting material, and wooden toys) with water and food \textit{ad libitum}. All animal protocols were designed in accordance with the National Institutes of Health Guide for the Care and Use of Laboratory Animals and were approved by the Institutional Animal Care and Use Committee at The University of Texas at Austin.

@@

Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function. After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

An additional subject ($n = 1$) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics. Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery. The timing of the anesthesia induction is identical to the protocol described above. The four repeated imaging sessions for this subject were spaced at least one week apart to minimize any complications from extended anesthesia exposure.

\subsection{Data Processing}

While head fixation can greatly minimize locomotion-associated brain movement \cite{Dombeck:2007gr}, it does not completely eliminate motion artifacts. The induction of general anesthesia also causes a major change in posture that can result in lateral displacements of the brain relative to the skull. In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery prior to fitting Eq.~(\ref{eq:mesi}). The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second. $ICT$ timecourses spanning the entire imaging session were also extracted from the fitted data from both vascular and parenchymal regions of interest.

In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) was estimated using the 5 ms exposure speckle contrast frames. Cross-sectional profiles were extracted from each vessel at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution. Because LSCI is most sensitive to moving scatterers, i.e. erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel. The vascular flux was then computed by scaling MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}. Relative changes in vascular flux and perfusion were calculated using the average of the entire awake state as the baseline.

@@

The systematic changes caused by general anesthesia with isoflurane are shown in Fig.~\ref{fig:system_image}b and Video 1. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}. Dilation can be seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature complicated image registration and precluded the generation of full-field relative flow change imagery.

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure1.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:system_image}
        (a) MESI system schematic with 2x magnification: L1 (f = 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 (f = 100 mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.). (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
    }
\end{figure}

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins and one parenchyma region were analyzed during the extended two-hour imaging session. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b. The width of the two vessels remained steady throughout the awake measurements but increased while under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c). The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%. The large deviation shortly after $t = 80$ min was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size. Repeated measurements in the subject (Fig.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:acute}
        (a) Awake speckle contrast image overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over an extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in the same animal over four imaging sessions (mean $\pm$ sd).
    }
\end{figure}

The repeatability of these measurements were further demonstrated across three additional subjects as shown in Fig.~\ref{fig:summary}. Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states over three separate imaging sessions lasting 30 minutes each. Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics. On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 1, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%). The perfusion of parenchymal regions increased on average by 80\% across all three subjects.

% Figure 3 - Awake to Anesthetized Results Summary
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure3.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:summary}
        Speckle contrast images from three awake subjects overlaid with vascular (R1 and R2) and parenchyma (R3 and R4) regions used during flow analysis. Dashed lines indicate the cross-sectional profiles used to calculate vessel width (Scale bar = 1 mm). Each row of charts depicts average vessel diameter, vascular flux, and parenchymal tissue perfusion during awake and anesthetized states across three different imaging sessions for each animal (mean $\pm$ sd).
    }
\end{figure}

@@

Much larger changes in blood flow were measured in the surface vessels, with vascular flux increasing on average by 135 $\pm$ 64\% across all trials. Even vessels that experienced only minimal vasodilation, such as R2 for Subject 1 in Fig.~\ref{fig:summary}, exhibited an over 60\% increase in flow. Because few imaging modalities are capable of measuring the dynamics of blood flow with sufficient spatial resolution to distinguish individual vessels, there has been limited work on this topic in awake animals. A lone study using laser Doppler flowmetry found only non-significant 18\% increases in both CBF and red blood cell (RBC) velocity in the barrel cortex after mice were anesthetized with isoflurane \cite{Takuwa:2012ee}. However, because large blood vessels were avoided, the laser Doppler measurements likely sampled smaller subsurface vasculature that may exhibit different responses to isoflurane than the larger surface vasculature imaged by MESI. The vascular flux metric calculated from the speckle correlation time is also not analogous to either the CBF or RBC velocity measured by laser Doppler flowmetry, so direct comparisons may not technically be possible \cite{Kazmi:2015du}.

@@

While LSCI has been utilized extensively with awake imaging \cite{Takuwa:2011jr,Seto:2014ga,Lu:2017bo,Balbi:2017cj,Sunil:2020ac}, this is one of the first uses of MESI in an awake animal model \cite{He:2020}. Traditional single-exposure LSCI would likely have underestimated the magnitude of the flow changes caused by isoflurane because individual exposure times are only sensitive to a range of flow rates \cite{Parthasarathy:2008el}. Failing to account for the increase in multiple dynamic scattering events caused by vasodilation would also have resulted in an underestimation of the flow changes in the visible surface vasculature. Using the raw $ICT$ value instead of the diameter-scaled vascular flux metric in Fig.~\ref{fig:acute}c would have measured only a 140\% increase in the large vessel instead of 267\%. The repeatability of the day-to-day measurements further demonstrate the robustness of MESI as a chronic blood flow imaging technique \cite{Kazmi:2013hp}, even when observing a fully-conscious, moving animal.

The effects of isoflurane fundamentally undermine the imaging of cortical hemodynamics in the normal physiological state. Blood flow imaging techniques such as LSCI, laser Doppler flowmetry, and fMRI require greater sensitivity because of the suppression of the hemodynamic response \cite{Takuwa:2012ee} and measure a delayed neurovascular coupling \cite{Pisauro:2013cx}. Anatomical imaging with two-photon microscopy only captures heavily-dilated vasculature unrepresentative of the awake resting state \cite{Lyons:2016bd}. The consistency and reliability of all imaging techniques can suffer from the effects of prolonged isoflurane exposure, which can cause continual vasodilation as seen in Fig.~\ref{fig:acute}b. This may result in extended imaging sessions documenting disparate anatomies and physiologies between the beginning and conclusion of an experiment.
